Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-02-28 manuscript.tex
Remove old manuscript file and minor fixes

\title{
Tesseroids: forward modeling gravitational fields in spherical coordinates
}
\righthead{Tesseroids}
% manuscript number
\ms{Submission}

@@

\address{
    \footnotemark[1]Universidade do Estado do Rio de Janeiro,
    Rio de Janeiro, Brazil.
    email: leouieda@gmail.com
}

@@

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in the open-source package \textit{Tesseroids}.
The software is freely available
on the Internet\footnote{http://www.leouieda.com/tesseroids}
under the BSD 3-clause license.
An archived version of the source code
is available as part of this article.

@@

Instead of using recursive function calls,
as originally proposed by \citet{Li2011},
we use a stack-based implementation of the algorithm.
Stacks are array-like data structures
with a particular way of inserting and removing elements from it.
In a stack,
one can only insert elements to the top of the stack
(the last empty position).
Likewise,
one can only remove the last element of the stack
(commonly referred to as ``popping'' the stack).
Stacks are also known as ``Last-in-first-out'', or LIFO, structures.

>>>>

\title{
Tesseroids: forward modeling gravitational fields in spherical coordinates
}
\righthead{Tesseroids}
\ms{Submission} % manuscript number

@@

\address{
    \footnotemark[1]Universidade do Estado do Rio de Janeiro,
    Rio de Janeiro, Brazil.
    email: leouieda@gmail.com
    \footnotemark[2]Observat\'orio Nacional,
    Rio de Janeiro, Brazil.
}

@@

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in the open-source package \textit{Tesseroids}.
The software is freely available
online\footnote{http://www.leouieda.com/tesseroids}
under the BSD 3-clause open-source license.
An archived version of the source code
is available as part of this article.

@@

Instead of using recursive function calls,
as originally proposed by \citet{Li2011},
we use a stack-based implementation of the algorithm.
Stacks are array-like data structures
with a particular way of inserting and removing elements from it.
In a stack,
one can only insert elements to the top of the stack
(the last empty position).
Likewise,
one can only remove the last element of the stack
(commonly referred to as ``popping'' the stack).
Stacks are also known as ``Last-in-first-out'', or LIFO, data structures.
